\documentclass{article}
\usepackage{amsmath,amssymb,amsthm,latexsym,paralist}

\theoremstyle{definition}
\newtheorem{problem}{Problem}
\newtheorem*{solution}{Solution}
\newtheorem*{resources}{Resources}

\newcommand{\name}[2]{\noindent\textbf{Name: #1}\hfill \textbf{UIN: #2}}
\newcommand{\honor}{\noindent On my honor, as an Aggie, I have neither
  given nor received any unauthorized aid on any portion of the
  academic work included in this assignment. Furthermore, I have
  disclosed all resources (people, books, web sites, etc.) that have
  been used to prepare this homework. \\[2ex]
 \textbf{Electronic signature: \underline{ (Type your full name here) } }}
 
\newcommand{\checklist}{\noindent\textbf{Checklist:}
\begin{compactitem}[$\Box$] 
\item Did you type in your name and UIN? 
\item Did you disclose all resources that you have used? \\
(This includes all people, books, websites, etc.\ that you have consulted.)
\item Did you sign that you followed the Aggie Honor Code? 
\item Did you solve all problems? 
\item Did you submit  the .tex and .pdf files of your homework to the correct link on eCampus? 
\end{compactitem}
}

\newcommand{\problemset}[1]{\begin{center}\textbf{Problem Set #1}\end{center}}
\newcommand{\duedate}[1]{\begin{quote}\textbf{Due dates:} Electronic
    submission of \textsl{yourLastName-yourFirstName-hw2.tex} and 
    \textsl{yourLastName-yourFirstName-hw2.pdf} files of this homework is due on
    \textbf{#1} on \texttt{http://ecampus.tamu.edu}. You will see two separate links
    to turn in the .tex file and the .pdf file separately. Please do not archive or compress the files.
    \textbf{If any of the two files are missing, you will likely receive zero points for this 
    homework.}\end{quote} }

\newcommand{\N}{\mathbf{N}}
\newcommand{\R}{\mathbf{R}}
\newcommand{\Z}{\mathbf{Z}}


\begin{document}
\vspace*{-15mm}
\begin{center}
{\large
CSCE 222 [Section 501] Discrete Structures for Computing\\[.5ex]
Spring 2019 -- Hyunyoung Lee\\}
\end{center}
\problemset{2}
\duedate{Wednesday, 2/6/2018, before 10:00 p.m.}
\name{(type your name here)}{(type your UIN here)}
\begin{resources} (All people, books, articles, web pages, etc.\ that
  have been consulted when producing your answers to this homework.)
\end{resources}
\honor

\bigskip

\noindent
\textbf{*** Please make sure that you are solving the correct problems from 
the \underline{8th Edition of the Rosen book}, not the 7th Edition! ***}

\medskip

\begin{problem} (5 points $\times$ 2 = 10 points) Section 1.4, Exercise 10 b) and c), page 57. 
\end{problem}
\begin{solution}
\end{solution}

\begin{problem} (5 points $\times$ 2 = 10 points) Section 1.4, Exercise 20 c) and d), page 57.
\end{problem}
\begin{solution}
\end{solution}

\begin{problem} (2.5 points $\times$ 4 = 10 points) Section 1.4, Exercise 36, page 58.
\end{problem}
\begin{solution}
\end{solution}

\begin{problem} (5 points $\times$ 4 = 20 points) Section 1.5, Exercise 28 a), b), c) and d), page 71. 
\textsl{Justify your answer or give a counterexample.}
\end{problem}
\begin{solution}
\end{solution}

\begin{problem} (10 points $\times$ 2 = 20 points) Section 1.6, Exercise 14 c) and d), page 83.
\end{problem}
\begin{solution}
\end{solution}

\begin{problem} (5 points) Section 1.7, Exercise 2, page 95. 
\end{problem}
\begin{solution}
\end{solution}

\begin{problem} (5 points) Section 1.7, Exercise 6, page 95.  
\end{problem}
\begin{solution}
\end{solution}

\begin{problem} (10 points) Prove by \textit{contradiction} that 
if $n\ge 1$ is a perfect square, then $n+2$ is not a perfect square. 
\end{problem}
\begin{solution}
\end{solution}

\begin{problem} (10 points) Prove by \textit{contradiction} that
at least three of any 25 days chosen must fall in the same month 
of the year.
\end{problem}
\begin{solution}
\end{solution} 

\goodbreak
\checklist
\end{document}
